---
title: "Test confounding factors of the negative correlation between genetic interaction profile similarity (GIPS) and interfacial overlap"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(svglite)
library(dplyr)
library(ggpubr)
library(forcats)
library(binr)
library(stringr)
library(boot)
knitr::opts_knit$set(root.dir = '~/Desktop/RealScience/data/processed/aim_2/')
```

# Functions

```{r functions}
standard_error <- function(x){
  se <- mean(replicate(1000, sd(sample(x, replace = TRUE)) / sqrt(length(x))))
  return(se)
}

low_boundary <- function(interval) {
  lowBoundary <- as.double(str_split(str_split(interval, ',')[[1]][1], '\\[')[[1]][2])
  return(lowBoundary)
}

high_boundary <- function(interval) {
  highBoundary <- as.double(str_split((str_split(str_split(interval, ',')[[1]][2], '\\]')[[1]][1]), ' ')[[1]][2])
  return(highBoundary)
}

calculate_which_bin <- function(column, boundaries_low, boundaries_high) {
  for (i in 1:length(boundaries_low)) {
    if (between(column, boundaries_low[i], boundaries_high[i]) == TRUE){
      return((boundaries_low[i] + boundaries_high[i]) / 2)
    }
  }
}

assign_bins <- function(x) {
  cuts <- bins(x$ORC, target.bins = 20, minpts = 10)
  boundaries_low <- unlist(lapply(names(cuts$binct), low_boundary))
  boundaries_high <- unlist(lapply(names(cuts$binct), high_boundary))
  result <- lapply(x$ORC, calculate_which_bin, boundaries_low = boundaries_low, boundaries_high = boundaries_high)
  x$bin <- unlist(result)
  return(x)
}

generate_PCC <- function(x) {
  cuts <- bins(x$ORC, target.bins = 20, minpts = 10)
  boundaries_low <- unlist(lapply(names(cuts$binct), low_boundary))
  boundaries_high <- unlist(lapply(names(cuts$binct), high_boundary))
  breaks <- append(boundaries_high, -1, 0)
  xaxis <- (boundaries_low + boundaries_high) / 2
  result <- tapply(x$GIPS, cut(x$ORC, breaks = breaks), mean)
  se <- tapply(x$GIPS, cut(x$ORC, breaks = breaks), standard_error)
  df <- data.frame(xaxis, result, se)
  return(df)
}

plot_original_PCC <- function(x) {
  p <- ggplot(x, aes(x=ORC, y=GIPS)) + 
    geom_point(size = 0.2) + 
    geom_smooth(method=lm, fullrange=TRUE) +  
    xlab('Interfacial overlap') + 
    ylab('Genetic interaction profile similarity') + 
    xlim(-1, 75) + ylim(-1, 1) + 
    theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14))
  return(p)
}

plot_PCC <- function(x) {
  model <- generate_wls(x)
  coeff <- coefficients(model)
  p <- ggplot(x, aes(x=xaxis, y=result, ymin=result - se, ymax=result + se)) + 
    geom_point() + 
    geom_errorbar(width = 0.2) + 
    geom_smooth(method="lm", mapping = aes(weight=1/se), se = FALSE, fullrange=TRUE) + 
    xlab('Interfacial overlap (binned)') + 
    ylab('Genetic interaction profile similarity') + 
    xlim(-1, 75) + ylim(-1, 1) + 
    theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14))
  return(p)
}

test_PCC <- function(x) {
  return(cor(x$xaxis, x$result))
}

pvalue_PCC <- function(x) {
  y <- cor.test(x$ORC, x$GIPS)
  return(y$p.value)
}

generate_wls <- function(x) {
  model <- lm(result ~ xaxis, data = x, weights = 1 / x$se)
  return(model)
}

lmp <- function (modelobject) {
    if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
    f <- summary(modelobject)$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    attributes(p) <- NULL
    return(p)
}

stats_weighted_PCC <- function(x) {
  model <- generate_wls(x)
  pvalue <- signif(lmp(model), 2)
  slope <- signif(model$coefficients[2], 2)
  r <- round(sqrt(summary(model)$r.squared),4)
  return(c(r, pvalue, slope))
}

stats_PCC <- function(df) {
  model <- lm(GIPS ~ ORC, data = df)
  pvalue <- lmp(model)
  slope <- model$coefficients[2]
  r <- sqrt(summary(model)$r.squared)
  return(c(r, pvalue, slope))
}
```

# Original correlation

```{r original}
df <- read.table('overlapping_residue_count_vs_genetic_GIPS.txt', header = 1)
df <- na.omit(df)
df <- assign_bins(df)
p1 <- plot_original_PCC(df)
stats_origin_raw <- stats_PCC(df)
p1 <- ggplot(df, aes(x=ORC, y=GIPS)) +
  geom_point(size = 0.2) +
  geom_smooth(method=lm, fullrange=TRUE) +
  xlab('Interfacial overlap') +
  ylab('Genetic interaction profile similarity') + 
  xlim(-1, 75) + ylim(0, 1) + 
  theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14))

x <- generate_PCC(df)
stats_origin_binned <- stats_weighted_PCC(x)
p2 <- plot_PCC(x)

# fractional interfacial overlap
p3 <- ggplot(df, aes(x=ORCR, y=GIPS)) + 
  geom_point(size = 0.2) + 
  geom_smooth(method=lm, fullrange=TRUE) +  
  xlab('Interfacial overlap ratio') + 
  ylab('Genetic interaction profile similarity') + 
  xlim(0, 1) + ylim(-1, 1) + 
  theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14))
# binning data
cuts <- bins(df$ORCR, target.bins = 20, minpts = 10)
boundaries_low <- unlist(lapply(names(cuts$binct), low_boundary))
boundaries_high <- unlist(lapply(names(cuts$binct), high_boundary))
breaks <- append(boundaries_high, -1, 0)
xaxis <- (boundaries_low + boundaries_high) / 2
result <- tapply(df$GIPS, cut(df$ORCR, breaks = breaks), mean)
se <- tapply(df$GIPS, cut(df$ORCR, breaks = breaks), standard_error)
x <- data.frame(xaxis, result, se)
pcc <- test_PCC(x)
pvalue <- pvalue_PCC(df)
# plot
p4 <- ggplot(x, aes(x=xaxis, y=result, ymin=result - se, ymax=result + se)) + 
    geom_point() + 
    geom_errorbar(width = 0.005) + 
    geom_smooth(method=lm, mapping = aes(weight = 1/se), se=FALSE, fullrange=TRUE) + 
    xlab('Interfacial overlap ratio (binned)') + 
    ylab('Genetic interaction profile similarity') + 
    xlim(-0.01, 1) + ylim(-1, 1) + 
    theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14))
p5 <- ggarrange(p1, p2, p3, p4, ncol=2, nrow=2, 
          labels = c('B', 'C', 'D', 'E'), 
          font.label = list(size=14, face='bold'))
ggsave('../../../figures/Origin_agged.svg', width = 10, height = 8, units = 'in')

# all GIs are considered
df <- read.table('all_overlapping_residue_count_vs_genetic_GIPS.txt', header = 1)
df <- na.omit(df)
stats_origin_ratio_raw <- stats_PCC(df)
p4 <- plot_original_PCC(df)
x <- generate_PCC(df)
pcc <- test_PCC(x)
pvalue <- pvalue_PCC(df)
modified_pvalue <- generate_pvalue(x, pcc)
stats_origin_ratio_binned <- stats_weighted_PCC(x)
p5 <- plot_PCC(x)
p6 <- ggarrange(p4, p5, ncol=2, nrow=1, 
          labels = c('A', 'B'), 
          font.label = list(size=14, face='bold'))
ggsave('../../../figures/Origin_all_GI_considered.svg', width = 10, height = 4, units = 'in')
```

# Essentiality

This section tests the effect of essentiality of both hubs and interactors on the negative correlation between GIPS and ORC. Specifically, this section is divided into two parts. We will sequentially investigate the effect of the followings: 1. The essentiality of hub; 2. The essentiality of interactors.

## Part I

```{r essentaility of hub}
df <- read.table('confounding_essentiality.txt', header = 1)
df <- na.omit(df)
names(df) <- c('hub', 'partner_1', 'partner_2', 'ORC', 'ORCR', 'GIPS', 'e.hub', 'e.partner_1', 'e.partner_2')

# Categorize data points according to the essentiality of hub
df_e_hub <- df[df$e.hub == 'essential',]
df_n_hub <- df[df$e.hub == 'non-essential',]

# Plot interfacial overlap against GIPS

## Essential hubs
p1 <- plot_original_PCC(df_e_hub)
stats_e_hub_raw <- stats_PCC(df_e_hub)
x_e_hub <- generate_PCC(df_e_hub)
stats_e_hub_binned <- stats_weighted_PCC(x_e_hub)
p2 <- plot_PCC(x_e_hub)

## Non-essential hubs
p3 <- plot_original_PCC(df_n_hub)
stats_n_hub_raw <- stats_PCC(df_n_hub)
x_n_hub <- generate_PCC(df_n_hub)
stats_n_hub_binned <- stats_weighted_PCC(x_n_hub)
p4 <- plot_PCC(x_n_hub)

p_hub_essentiality <- ggarrange(p1, p2, p3, p4, 
                                ncol=2, nrow=2, 
                                labels = c('A', 'B', 'C', 'D'), 
                                font.label = list(size=14, face='bold'))
ggsave('../../../figures/essentiality_hub.svg', width = 10, height = 8, units = 'in')
```

## Part II

```{r essentiality of partner}
# Categorize data points according to the essentiality of hub
df_e_partner <- df[(df$e.partner_1 == 'essential') & (df$e.partner_2 == 'essential'),]
df_i_partner <- df[((df$e.partner_1 == 'essential') & (df$e.partner_2 == 'non-essential')) | 
                     ((df$e.partner_1 == 'non-essential') & (df$e.partner_2 == 'essential')),]
df_n_partner <- df[(df$e.partner_1 == 'non-essential') & (df$e.partner_2 == 'non-essential'),]

# Plot interfacial overlap against GIPS

## A pair of essential partners
stats_e_partner_raw <- stats_PCC(df_e_partner)
x_e_partner <- generate_PCC(df_e_partner)
p1 <- plot_original_PCC(df_e_partner)
stats_e_partner_binned <- stats_weighted_PCC(x_e_partner)
p2 <- plot_PCC(x_e_partner)

## Essential + non-essential
stats_i_partner_raw <- stats_PCC(df_i_partner)
x_i_partner <- generate_PCC(df_i_partner)
p3 <- plot_original_PCC(df_i_partner)
stats_i_partner_binned <- stats_weighted_PCC(x_i_partner)
p4 <- plot_PCC(x_i_partner)

## A pair of non-essential partners
stats_n_partner_raw <- stats_PCC(df_n_partner)
x_n_partner <- generate_PCC(df_n_partner)
p5 <- plot_original_PCC(df_n_partner)
stats_n_partner_binned <- stats_weighted_PCC(x_n_partner)
p6 <- plot_PCC(x_n_partner)

p_partner_essentiality <- ggarrange(p1, p2, p3, p4, p5, p6, 
                                    ncol=2, nrow=3, 
                                    labels = c('A', 'B', 'C', 'D', 'E', 'F'), 
                                    font.label = list(size=14, face='bold'))
ggsave('../../../figures/essentiality_partner.svg', width = 10, height = 12, units = 'in')
```

# Sequence similarity

This section tests the effect of sequence similarity of interactors on the negative correlation between GIPS and ORC. Specifically, this section is divided into two parts. We will sequentially investigate the effect of the followings: 1. The global sequence similarity of whole interactors; 2. The interfacial sequence similarity of interactors.

## Part I

```{r global sequence similarity}
df_identities <- read.table('identities_positives_structural_interactome.txt')
df_identities <- na.omit(df_identities)
threshold <- 3e-10
df_seq_h <- df_identities[df_identities$Evalue >= threshold,]
df_seq_l <- df_identities[df_identities$Evalue < threshold,]
df_seq_very_h <- df_identities[df_identities$Evalue >= 1,]

# High sequence similarity
stats_seq_l_raw <- stats_PCC(df_seq_l)
x_seq_l <- generate_PCC(df_seq_l)
p1 <- plot_original_PCC(df_seq_l)
stats_seq_l_binned <- stats_weighted_PCC(x_seq_l)
p2 <- plot_PCC(x_seq_l)

# Low sequence similarity
stats_seq_h_raw <- stats_PCC(df_seq_h)
x_seq_h <- generate_PCC(df_seq_h)
p3 <- plot_original_PCC(df_seq_h)
stats_seq_h_binned <- stats_weighted_PCC(x_seq_h)
p4 <- plot_PCC(x_seq_h)

# Very low sequence similarity
stats_seq_very_h_raw <- stats_PCC(df_seq_very_h)
x_seq_very_h <- generate_PCC(df_seq_very_h)
p5 <- plot_original_PCC(df_seq_very_h)
stats_seq_very_h_binned <- stats_weighted_PCC(x_seq_very_h)
p6 <- plot_PCC(x_seq_very_h)

p_seq <- ggarrange(p1, p2, p3, p4, p5, p6, 
                   ncol=2, nrow=3, 
                   labels = c('A', 'B', 'C', 'D', 'E', 'F'), 
                   font.label = list(size=14, face='bold'))
ggsave('../../../figures/seqsim_global.svg', width = 10, height = 12, units = 'in')
```

## Part II

```{r local sequence similarity}
df_identities_local <- read.table('confounding_sequence_similarity_local_new_50.txt', header = 1)
df_identities_local <- na.omit(df_identities_local)

threshold <- 3e-10
df_seq_local_h <- df_identities_local[df_identities_local$E.value >= threshold,]
df_seq_local_l <- df_identities_local[df_identities_local$E.value < threshold,]

# High sequence similarity
stats_seq_local_l_raw <- stats_PCC(df_seq_local_l)
x_seq_local_l <- generate_PCC(df_seq_local_l)
p1 <- plot_original_PCC(df_seq_local_l)
stats_seq_local_l_binned <- stats_weighted_PCC(x_seq_local_l)
p2 <- plot_PCC(x_seq_local_l)

# Low sequence similarity
stats_seq_local_h_raw <- stats_PCC(df_seq_local_h)
x_seq_local_h <- generate_PCC(df_seq_local_h)
p3 <- plot_original_PCC(df_seq_local_h)
stats_seq_local_h_binned <- stats_weighted_PCC(x_seq_local_h)
p4 <- plot_PCC(x_seq_local_h)

p_seq_local <- ggarrange(p1, p2, p3, p4, 
                         ncol=2, nrow=2, 
                         labels = c('A', 'B', 'C', 'D'), 
                         font.label = list(size=14, face='bold'))
ggsave('../../../figures/seqsim_local.svg', width = 10, height = 8, units = 'in')
```

# Structural similarity

This section tests the effect of structural similarity of interactors on the negative correlation between GIPS and ORC. Specifically, this section is divided into two parts. We will sequentially investigate the effect of the followings: 1. The global structural similarity of whole interactors; 2. The structural similarity of interfaciali structural similarity of interactors.

## Part I

```{r global structural similarity}
df_strsim <- read.table('confounding_structural_similarity.txt', header = 1)
df_strsim <- na.omit(df_strsim)
df_strsim_h <- df_strsim[df_strsim$TM.score > 0.5,]
df_strsim_m <- df_strsim[(df_strsim$TM.score >= 0.3) & (df_strsim$TM.score <= 0.5),]
df_strsim_l <- df_strsim[df_strsim$TM.score < 0.3,]

# High structural similarity
stats_strsim_h_raw <- stats_PCC(df_strsim_h)
x_strsim_h <- generate_PCC(df_strsim_h)
p1 <- plot_original_PCC(df_strsim_h)
stats_strsim_h_binned <- stats_weighted_PCC(x_strsim_h)
p2 <- plot_PCC(x_strsim_h)

# Intermediate structural similarity
stats_strsim_m_raw <- stats_PCC(df_strsim_m)
x_strsim_m <- generate_PCC(df_strsim_m)
p3 <- plot_original_PCC(df_strsim_m)
stats_strsim_m_binned <- stats_weighted_PCC(x_strsim_m)
p4 <- plot_PCC(x_strsim_m)

# Low structural similarity
stats_strsim_l_raw <- stats_PCC(df_strsim_l)
x_strsim_l <- generate_PCC(df_strsim_l)
p5 <- plot_original_PCC(df_strsim_l)
stats_strsim_l_binned <- stats_weighted_PCC(x_strsim_l)
p6 <- plot_PCC(x_strsim_l)

p_str <- ggarrange(p1, p2, p3, p4, p5, p6, 
                   ncol=2, nrow=3, 
                   labels = c('A', 'B', 'C', 'D', 'E', 'F'), 
                   font.label = list(size=14, face='bold'))
ggsave('../../../figures/strsim_global.svg', width = 10, height = 12, units = 'in')
```

## Part II

```{r local structural similarity}
df_strsim_local <- read.table('confounding_structural_similarity_local_new_50_30_10.txt', header = 1)
df_strsim_local <- na.omit(df_strsim_local)
names(df_strsim_local) <- c('hub', 'Protein_1', 'Protein_2', 'ORC', 'ORCR', 'GIPS', 'TM.score', 'TM.score_30', 'TM.score_10')
df_strsim_local <- df_strsim_local[df_strsim_local$TM.score > 0,]
df_strsim_local_h <- df_strsim_local[df_strsim_local$TM.score > 0.5,]
df_strsim_local_m <- df_strsim_local[(df_strsim_local$TM.score >= 0.3) & (df_strsim_local$TM.score <= 0.5),]
df_strsim_local_l <- df_strsim_local[df_strsim_local$TM.score < 0.3,]
df_strsim_local_l_extended <- read.table('All_TM-scores.txt', header = 1)
df_strsim_local_l_extended <- na.omit(df_strsim_local_l_extended)
df_strsim_local_l_extended <- df_strsim_local_l_extended[((df_strsim_local_l_extended$TM.score_50 < 0.3) & 
                                                            (df_strsim_local_l_extended$TM.score_50 > 0)) |
                                                           ((df_strsim_local_l_extended$TM.score_50 < 0) & 
                                                            (df_strsim_local_l_extended$TM.score_entire < 0.3)),]

# High structural similarity
stats_strsim_local_h_raw <- stats_PCC(df_strsim_local_h)
x_strsim_local_h <- generate_PCC(df_strsim_local_h)
p1 <- plot_original_PCC(df_strsim_local_h)
stats_strsim_local_h_binned <- stats_weighted_PCC(x_strsim_local_h)
p2 <- plot_PCC(x_strsim_local_h)

# Intermediate structural similarity
stats_strsim_local_m_raw <- stats_PCC(df_strsim_local_m)
x_strsim_local_m <- generate_PCC(df_strsim_local_m)
p3 <- plot_original_PCC(df_strsim_local_m)
stats_strsim_local_m_binned <- stats_weighted_PCC(x_strsim_local_m)
p4 <- plot_PCC(x_strsim_local_m)

# Low structural similarity
stats_strsim_local_l_raw <- stats_PCC(df_strsim_local_l)
x_strsim_local_l <- generate_PCC(df_strsim_local_l)
p5 <- plot_original_PCC(df_strsim_local_l)
stats_strsim_local_l_binned <- stats_weighted_PCC(x_strsim_local_l)
p6 <- plot_PCC(x_strsim_local_l)

# Extended low structural similarity
stats_strsim_local_l_extended_raw <- stats_PCC(df_strsim_local_l_extended)
x_strsim_local_l_extended <- generate_PCC(df_strsim_local_l_extended)
p01 <- plot_original_PCC(df_strsim_local_l_extended)
stats_strsim_local_l_extended_binned <- stats_weighted_PCC(x_strsim_local_l_extended)
p02 <- plot_PCC(x_strsim_local_l_extended)

p_str_local <- ggarrange(p1, p2, p3, p4, p01, p02, 
                         ncol=2, nrow=3, 
                         labels = c('A', 'B', 'C', 'D', 'E', 'F'), 
                         font.label = list(size=14, face='bold'))
ggsave('../../../figures/strsim_local.svg', width = 10, height = 12, units = 'in')
```

# Functions for plotting GO similarity

```{r functions for plotting GO similarity}
plot_PCC_GO <- function(x, y) {
  model <- generate_wls(x)
  coeff <- coefficients(model)
  p <- ggplot(x, aes(x=xaxis, y=result, ymin=result - se, ymax=result + se)) + 
    geom_point() + 
    geom_errorbar(width = 0.2) + 
    geom_smooth(method="lm", mapping = aes(weight=1/se), se = FALSE, fullrange=TRUE) + 
    xlab('Interfacial overlap (binned)') + 
    ylab(y) + 
    xlim(-1, 75) + ylim(0, 1) + 
    theme(axis.text = element_text(size = 13), axis.title = element_text(size = 11))
  return(p)
}

stats_PCC_GO_mf <- function(df) {
  model <- lm(mf ~ ORC, data = df)
  pvalue <- lmp(model)
  slope <- model$coefficients[2]
  r <- sqrt(summary(model)$r.squared)
  return(c(r, pvalue, slope))
}

stats_PCC_GO_bp <- function(df) {
  model <- lm(bp ~ ORC, data = df)
  pvalue <- lmp(model)
  slope <- model$coefficients[2]
  r <- sqrt(summary(model)$r.squared)
  return(c(r, pvalue, slope))
}

stats_PCC_GO_cc <- function(df) {
  model <- lm(cc ~ ORC, data = df)
  pvalue <- lmp(model)
  slope <- model$coefficients[2]
  r <- sqrt(summary(model)$r.squared)
  return(c(r, pvalue, slope))
}

generate_PCC_GO_mf <- function(x) {
  cuts <- bins(x$ORC, target.bins = 20, minpts = 10)
  boundaries_low <- unlist(lapply(names(cuts$binct), low_boundary))
  boundaries_high <- unlist(lapply(names(cuts$binct), high_boundary))
  breaks <- append(boundaries_high, -1, 0)
  xaxis <- (boundaries_low + boundaries_high) / 2
  result <- tapply(x$mf, cut(x$ORC, breaks = breaks), mean)
  se <- tapply(x$mf, cut(x$ORC, breaks = breaks), standard_error)
  df <- data.frame(xaxis, result, se)
  return(df)
}

generate_PCC_GO_bp <- function(x) {
  cuts <- bins(x$ORC, target.bins = 20, minpts = 10)
  boundaries_low <- unlist(lapply(names(cuts$binct), low_boundary))
  boundaries_high <- unlist(lapply(names(cuts$binct), high_boundary))
  breaks <- append(boundaries_high, -1, 0)
  xaxis <- (boundaries_low + boundaries_high) / 2
  result <- tapply(x$bp, cut(x$ORC, breaks = breaks), mean)
  se <- tapply(x$bp, cut(x$ORC, breaks = breaks), standard_error)
  df <- data.frame(xaxis, result, se)
  return(df)
}

generate_PCC_GO_cc <- function(x) {
  cuts <- bins(x$ORC, target.bins = 20, minpts = 10)
  boundaries_low <- unlist(lapply(names(cuts$binct), low_boundary))
  boundaries_high <- unlist(lapply(names(cuts$binct), high_boundary))
  breaks <- append(boundaries_high, -1, 0)
  xaxis <- (boundaries_low + boundaries_high) / 2
  result <- tapply(x$cc, cut(x$ORC, breaks = breaks), mean)
  se <- tapply(x$cc, cut(x$ORC, breaks = breaks), standard_error)
  df <- data.frame(xaxis, result, se)
  return(df)
}
```

# Compare different functional similarity measurements

```{r compare functional similarity}
# plot ORC vs. GO-based semantic similarity
compare_functional_similarity_ORC <- read.table('overlapping_residue_count_vs_semetic_similarity.txt', header = 1)
compare_functional_similarity_ORC <- na.omit(compare_functional_similarity_ORC)
p1 <- ggplot(compare_functional_similarity_ORC, aes(x=ORC, y=mf)) + 
  geom_point(size = 0.2) + 
  geom_smooth(method=lm, fullrange=TRUE) +  
  xlab('Interfacial overlap') + 
  ylab('Semantic similarity (GO Molecular Function)') + 
  xlim(-1, 75) + ylim(0, 1) + 
  theme(axis.text = element_text(size = 13), axis.title = element_text(size = 11))
x1 <- generate_PCC_GO_mf(compare_functional_similarity_ORC)
stats_mf_origin <- stats_PCC_GO_mf(compare_functional_similarity_ORC)
stats_mf_binned <- stats_weighted_PCC(x1)
p11 <- plot_PCC_GO(x1, 'Semantic similarity (GO Molecular Function)')


p2 <- ggplot(compare_functional_similarity_ORC, aes(x=ORC, y=bp)) + 
  geom_point(size = 0.2) + 
  geom_smooth(method=lm, fullrange=TRUE) +  
  xlab('Interfacial overlap') + 
  ylab('Semantic similarity (GO Biological Process)') + 
  xlim(-1, 75) + ylim(0, 1) + 
  theme(axis.text = element_text(size = 13), axis.title = element_text(size = 11))
x2 <- generate_PCC_GO_bp(compare_functional_similarity_ORC)
stats_bp_origin <- stats_PCC_GO_bp(compare_functional_similarity_ORC)
stats_bp_binned <- stats_weighted_PCC(x2)
p21 <- plot_PCC_GO(x2, 'Semantic similarity (GO Biological Process)')


p3 <- ggplot(compare_functional_similarity_ORC, aes(x=ORC, y=cc)) + 
  geom_point(size = 0.2) + 
  geom_smooth(method=lm, fullrange=TRUE) +  
  xlab('Interfacial overlap') + 
  ylab('Semantic similarity (GO Cellular Component)') + 
  xlim(-1, 75) + ylim(0, 1) + 
  theme(axis.text = element_text(size = 13), axis.title = element_text(size = 11))
x3 <- generate_PCC_GO_cc(compare_functional_similarity_ORC)

stats_cc_origin <- stats_PCC_GO_cc(compare_functional_similarity_ORC)
stats_cc_binned <- stats_weighted_PCC(x3)
p31 <- plot_PCC_GO(x3, 'Semantic similarity (GO Cellular Component)')

p5 <- ggarrange(p1, p11, p2, p21, p3, p31, 
                ncol=2, nrow=3, 
                labels = c('A', 'B', 'C', 'D', 'E', 'F'), 
                font.label = list(size=14, face='bold'))
ggsave('../../../figures/Functional_similarity_measurement.jpg', width = 10, height = 12)


compare_functional_similarity <- read.table('compare_functional_similarity.txt', header = 1)
compare_functional_similarity <- na.omit(compare_functional_similarity)
wilcox.test(compare_functional_similarity[compare_functional_similarity$ORC > 0,]$GIPS, 
            compare_functional_similarity[compare_functional_similarity$ORC == 0,]$GIPS)

compare_functional_similarity$ORC[compare_functional_similarity$ORC > 0] <- 1
comp <- compare_functional_similarity %>% group_by(ORC) %>%
  summarise(mean_GIPS=mean(GIPS), 
            mean_bp=mean(bp), 
            mean_mf=mean(mf), 
            mean_cc=mean(cc), 
            se_GIPS=standard_error(GIPS), 
            se_bp=standard_error(bp), 
            se_mf=standard_error(mf), 
            se_cc=standard_error(cc), 
            .groups = 'drop') %>%
  as.data.frame()
classified <- c('No shared target protein', 'Simultaneously possible', 'Mutually exclusive')
mean_list <- c(as.numeric(comp[1,2:5]), as.numeric(comp[2,2:5]), as.numeric(comp[3,2:5]))
se_list <- c(as.numeric(comp[1,6:9]), as.numeric(comp[2,6:9]), as.numeric(comp[3,6:9]))
comp_result <- data.frame(class=rep(classified, each=4), 
                          Measurement=rep(c('Genetic interaction profile similarity', 'GO Biological Process', 'GO Molecular Function', 'GO Cellular Component'), 3), 
                          mean=mean_list, 
                          se=se_list)

comp_result$class <- factor(comp_result$class, levels = c('No shared target protein', 'Simultaneously possible', 'Mutually exclusive'))
comp_result$Measurement <- factor(comp_result$Measurement, levels = c('GO Cellular Component', 'GO Molecular Function', 'GO Biological Process', 'Genetic interaction profile similarity'))

p4 <- ggplot(data=comp_result, aes(x=class, y=mean, fill=Measurement)) + 
  geom_bar(stat='identity', color='black', position=position_dodge()) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, 
                position=position_dodge(.9)) + 
  xlab('Relationship of interactors') + 
  ylab('Functional similarity') + 
  theme_bw() + 
  theme(axis.text = element_text(size = 13), 
        axis.title = element_text(size = 15), 
        legend.text = element_text(size = 13), 
        legend.position = c(0.65, 0.18), 
        panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) + 
  scale_y_continuous(expand = c(0,0),limits = c(0, 0.49)) + 
  coord_flip()
ggsave('../../../figures/Functional_similarity_measurement_3.svg', width = 7, height = 6)
#  scale_fill_manual(values=c("#597C8B", "#DABE84", "#E69F00"))

## Scatter plot: interfacial overlap vs. semantic similarity (bp)
ggplot(compare_functional_similarity, aes(x=ORC, y=bp)) + 
  geom_point(size = 0.2) + 
  geom_smooth(method=lm, fullrange=TRUE) +  
  xlab('Interfacial overlap') + 
  ylab('Semantic similarity (GO Biological Process')

## Scatter plot: interfacial overlap vs. semantic similarity (mf)
ggplot(compare_functional_similarity, aes(x=ORC, y=mf)) + 
  geom_point(size = 0.2) + 
  geom_smooth(method=lm, fullrange=TRUE) +  
  xlab('Interfacial overlap') + 
  ylab('Semantic similarity (GO Molecular Function')
```

# Plot the number table

```{r number}
library(data.table)
cells <- data.frame(stats_origin_binned, stats_e_hub_binned, stats_n_hub_binned, 
           stats_e_partner_binned, stats_n_partner_binned, stats_i_partner_binned, 
           stats_seq_l_binned, stats_seq_h_binned, stats_seq_very_h_binned, 
           stats_seq_local_l_binned, stats_seq_local_h_binned, 
           stats_strsim_h_binned, stats_strsim_m_binned, stats_strsim_l_binned, 
           stats_strsim_local_h_binned, stats_strsim_m_binned, stats_strsim_local_l_extended_binned)
cells <- transpose(cells)
names(cells) <- c("r", "p-value", "slope")
write.table(cells, file = "../../../figures/binned_numbers.txt", sep = '\t', quote = FALSE)
```

# Plot genetic interaction profiles for case studies

```{r GIP}
GIP1 <- read.table('~/Desktop/RealScience/data/processed/GIP_YDR334W_YML041C.txt', header=1)
p1 <- ggplot(GIP1, aes(x=YML041C, y=YDR334W)) + 
    geom_point(size = 0.2) + 
    xlab('SWC6') + 
    ylab('SWR1') + 
    xlim(-1, 1) + ylim(-1, 1) + 
    theme_bw() + 
    theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14), 
          panel.border = element_blank(), panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
ggsave('../../../figures/YDR334W_YML041C.jpg', width = 4, height = 4, units = 'in')
GIP2 <- read.table('~/Desktop/RealScience/data/processed/GIP_YLL024C_YAL005C.txt', header=1)
p2 <- ggplot(GIP2, aes(x=YAL005C, y=YLL024C)) + 
    geom_point(size = 0.2) + 
    xlab('SSA1') + 
    ylab('SSA2') + 
    xlim(-1, 1) + ylim(-1, 1) + 
    theme_bw() + 
    theme(axis.text = element_text(size = 13), axis.title = element_text(size = 14), 
          panel.border = element_blank(), panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
ggsave('../../../figures/YLL024C_YAL005C.jpg', width = 4, height = 4, units = 'in')
```
